Concurrent Programming with CXL

### 2020-06-05 book/paper.tex
Latest

@@

[TODO.  The following must be updated.]
CXL does not complain about Figure~\ref{fig:rwbusy}, but using
the right test, CXL can be used to check for busy-waiting.
One approach is as follows.  First, obtain a lock in the initialization
code by adding the following line to the end of the code:
\begin{code}
\begin{verbatim}
call acquire_rlock();
\end{verbatim}
\end{code}

Second, run CXL with the \texttt{-b} flag.  This flag tells CXL to check
that all states are non-terminating and have all processes blocked.

@@

>>>>

\begin{figure}
\begin{code}
\VerbatimInput[xleftmargin=5mm,numbers=left]{../RWblock.cxl}
\end{code}
\caption{Checking for Busy Waiting.}
\label{fig:rwblock}
\end{figure}

@@

CXL does not complain about Figure~\ref{fig:rwbusy}, but, using
the right test, CXL can be used to check for busy-waiting.
Figure~\ref{fig:rwblock} presents such a test.
Note that the initialization code obtains a read lock, preventing
all readers and writers from entering the critical section.
In that case, those processes should ideally be blocked and CXL
can test for that by running it with the \texttt{-b} flag.
This flag tells CXL to check
that all states are non-terminating and have all processes blocked.

@@

\begin{quote}
\begin{itemize}
\item Why do you suppose the code in Figure~\ref{fig:rwmulti} uses a flag
per process rather than a simple counter?
\item Can you write a version of this test that uses a counter instead
of a flag per process?
\end{itemize}
\end{quote}
